---
title: "BCB546-Spring 2022-Project"
author: "Ann Murithi", "Fazihr Kayondo ""Ceren Ordas", "Stephen Gray", "Mercy Fakude"
date: "5/3/2022"
output: html_document
---
#FINAL PROJECT#

## Data Processing (Done using Python)
1. Import data 
2. Check data structure using .shape command
3. Check data frame using type command
4. Check data type per column using .dtype command
5. view column headers using .column command
6. View the first six rown and last rows using .head and .tail command

```{r setup, include=FALSE}
import pandas as pd
s2_data = pd.read_csv('S2_Dataset.csv')
s2_data
type(s2_data)
s2_data.dtypes
s2_data.columns
s2_data.head(6)
s2_data.tail(6)
```


## Data summary
```{r cars}
RPKM = s2_data.groupby(['RPKM-Group NI', 'RPKM-Group I'])
RPKM['GeneID'].describe()
regulation = s2_data.groupby('Up-Down-Regulation(Group I/Group NI)')
regulation['GeneID'].describe()
Genes_regulation = s2_data.groupby('Up-Down-Regulation(Group I/Group NI)')['GeneID'].nunique()
Genes_regulation.plot(kind ='bar', title='gene_regulation')
```


## Visualizing
1. import all the packages required for thie work
```{r pressure, echo=FALSE}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
```
## Plot for distributuin of gene legnth of the DE genes 
```{r pressure, echo=FALSE}
s2_data.head(2)
sns.displot(s2_data['Gene Length'], color='c',bins=50, 
            height=7, aspect=1)
```
## Ploting without index 56
1. Remove row/index 56 (the gene is an outlier)
2. plot RPKM for Group I againg Group NI
3. Plot the log2ration against gene length
```{r pressure, echo=FALSE}
s2_data2 = s2_data.drop([56])
s2_data2.shape
sns.lmplot(x="RPKM-Group NI", y="RPKM-Group I", data=s2_data2, fit_reg=False, height=7, aspect=1, scatter_kws={'alpha':0.9,"s": 60}, 
           hue='Up-Down-Regulation(Group I/Group NI)', markers='D')
sns.lmplot(x='log2Ratio(Group I/Group NI)', y="Gene Length", data=s2_data2, fit_reg=False, height=7, aspect=1, scatter_kws={'alpha':0.7,"s": 60}, 
           hue='Up-Down-Regulation(Group I/Group NI)', markers='D')
```

```{r pressure, echo=FALSE}
plot(pressure)
```

```{r pressure, echo=FALSE}
plot(pressure)
```

```{r pressure, echo=FALSE}
plot(pressure)
```
