---
title: Gene Ontology Analysis
author: #Reading CSV file, Subsetting, and Merging Data for GO analysis 
date: "5/6/2022"
output: html_document
---

```{r}
#Install Packages For Analysis 
install.packages("ggplot2")
install.packages("tidyr")
install.packages("dplyr")
install.packages("tidyverse")
install.packages("ggpubr")
install.packages("patchwork")
install.packages("egg")
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggpubr)
library(patchwork)
library(egg)

```



#Reading CSV file, Subsetting, and Merging Data for GO analysis 
```{r}
gene_onto= read.csv("my_dat_3.csv", fileEncoding = "UTF-8-BOM", header = T)

```


#Subsetting Data Based on Ontology Function 
```{r}
gene_onto_subset= subset(gene_onto,select= c(EntrezID,Gene.Ontology,Function))
gene_onto_group= gene_onto_subset %>% group_by(Gene.Ontology)
GroupCount=gene_onto_group %>%
  count(Function)
GroupCount_Split=split(GroupCount, GroupCount$Gene.Ontology)
Biological=GroupCount_Split$Biological
Molecular=GroupCount_Split$Molecular
Cellular=GroupCount_Split$Cellular
```


#Gene Ontology BarPlot
```{r}
Bio=ggplot(data= Biological,aes(x=n, y=Function))+
  geom_bar(stat="identity",width = 0.3, fill="Blue")+
  ylab(NULL)+
  xlab(NULL)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
Mol=ggplot(data= Molecular,aes(x=n, y=Function))+
  geom_bar(stat="identity", width= 0.3,  fill="Yellow")+
  ylab("Gene Function")+
  xlab(NULL)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
Cell=ggplot(data= Cellular,aes(x=n, y=Function))+
  geom_bar(stat="identity", width = 0.3, fill="Brown")+
  ylab(NULL)+
  xlab("Number of Genes")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggarrange(Bio, Mol, Cell,
          labels = c("Bio","Mol","Cell"),
          ncol = 1, nrow = 3)

```






---
title: Kegg Analysis 
author:"Ann Murithi", "Fazihr Kayondo ""Ceren Ordas", "Stephen Gray", "Mercy Fakude"
date: "5/6/2022"
output: html_document
---



#R PACKAGE FOR KEGG ANALYSIS:
```{r}
install.packages("pathfindR")
library(pathfindR)
```


#Download data frame:
```{r}
library(readxl)
DataforEnrichment <- read_excel("DataforEnrichment.xlsx", col_types = c("text", "numeric", "numeric", "text", "text"))
View(DataforEnrichment)
```

#Make enrichment chart:This code gives us the enrichment chart for the top 20 terms, just like they did in the original paper, but we are not able to customize our data with this code so I used another code later on.

```{r}
enrichment_chart(result_df = DataforEnrichment, top_terms = 20)
```

#Using ggplot to make the enrichment chart with top 20 terms and using a blue color gradient just like the authors did on the original paper.

```{r}
library(ggplot2)
g <- enrichment_chart(DataforEnrichment, top_terms = 20)
g <- g + scale_color_gradient(low = "black", high = "blue")
g
```





title: Validation of Gene Expression  
author:"Ann Murithi", "Fazihr Kayondo ""Ceren Ordas", "Stephen Gray", "Mercy Fakude"
date: "5/6/2022"
output: html_document

#You will have to download the raw dataset showing gene expression called "raw_gene_data.xlsx" into your working directory. This is available on GitHub
#Reproducing Fig.4 


#Load packages
```{r}
#install.packages("plotly")
#install.packages("tidyverse")
library(tidyverse)
library(dplyr)
library(plotly)
library(readxl)
```


#Import the dataset
```{r}
raw_gene_data <- read_excel("raw_gene_data.xlsx")
raw_gene_data$Ref_up <- raw_gene_data$`RPKM-Group I` / raw_gene_data$`RPKM-Group NI`
std = sapply(raw_gene_data[c('Ref_up')], sd) #this computes the standard deviation of the fold changes (Ref_up)
raw_gene_data$"SD" <- NA
raw_gene_data[["SD"]] <- raw_gene_data$`Probability` * (std/100) #This Standard deviation is my own version not the actual one
```


#Random selection of the genes
```{r}
selected_genes <- raw_gene_data[c(23, 29, 11, 80, 4, 45, 14, 74, 59, 26), ]
PBS.Reference = data.frame(PBS.Reference = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1)) # I used "1" for all the values just by inference. We were not provided with this information
semi_final_df <- cbind(selected_genes, PBS.Reference)
```


#Assigning names of selected genes
```{r}
gene_name = data.frame(gene_name = c('NADH4', 'ATP8', 'MRPS23', 'DCTN2', 'C1QA', 'CD209', 'CAPG', 'APRT', 'CEBPE', 'RPS12'))
final_df <- cbind(semi_final_df, gene_name)
```

#Visualization of the selected genes; Plotting with `Plotly`
```{r}
library(plotly)
fig <- plot_ly(final_df, x = ~gene_name, y = ~Ref_up, type = 'bar', name = 'FMDV', marker = list(color = 'red'), error_y = list(array=~SD))
fig <- fig %>% add_trace(y = ~PBS.Reference, name = 'PBS', marker = list(color = 'black'))
fig <- fig %>% layout(yaxis = list(title = 'Relative expression'), barmode = 'group', bargap = 0.20, bargroupgap = 0.45)
fig
```




