---
title: "Gene Ontology Analysis" and Kegg Analysis 
author: Stephen Gray
date: "5/6/2022"
output: html_document
---

```{r}
#Install Packages For Analysis 
install.packages("ggplot2")
install.packages("tidyr")
install.packages("dplyr")
install.packages("tidyverse")
install.packages("ggpubr")
install.packages("patchwork")
install.packages("egg")
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggpubr)
library(patchwork)
library(egg)

```




```{r}
#Reading CSV file, Subsetting, and Merging Data for GO analysis 
gene_onto= read.csv("my_dat_3.csv", fileEncoding = "UTF-8-BOM", header = T)

```



```{r}
#Subsetting Data Based on Ontology Function 
gene_onto_subset= subset(gene_onto,select= c(EntrezID,Gene.Ontology,Function))
gene_onto_group= gene_onto_subset %>% group_by(Gene.Ontology)
GroupCount=gene_onto_group %>%
  count(Function)
GroupCount_Split=split(GroupCount, GroupCount$Gene.Ontology)
Biological=GroupCount_Split$Biological
Molecular=GroupCount_Split$Molecular
Cellular=GroupCount_Split$Cellular
```



```{r}
#Gene Ontology BarPlot
Bio=ggplot(data= Biological,aes(x=n, y=Function))+
  geom_bar(stat="identity",width = 0.3, fill="Blue")+
  ylab(NULL)+
  xlab(NULL)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
Mol=ggplot(data= Molecular,aes(x=n, y=Function))+
  geom_bar(stat="identity", width= 0.3,  fill="Yellow")+
  ylab("Gene Function")+
  xlab(NULL)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
Cell=ggplot(data= Cellular,aes(x=n, y=Function))+
  geom_bar(stat="identity", width = 0.3, fill="Brown")+
  ylab(NULL)+
  xlab("Number of Genes")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggarrange(Bio, Mol, Cell,
          labels = c("Bio","Mol","Cell"),
          ncol = 1, nrow = 3)

```






---
title: Kegg Analysis 
author:Ceren Ordas
date: "5/6/2022"
output: html_document
---



#R PACKAGE FOR KEGG ANALYSIS:
```{r}
install.packages("pathfindR")
library(pathfindR)
```


#Download data frame:
```{r}
library(readxl)
DataforEnrichment <- read_excel("DataforEnrichment.xlsx", col_types = c("text", "numeric", "numeric", "text", "text"))
View(DataforEnrichment)
```

#Make enrichment chart:This code gives us the enrichment chart for the top 20 terms, just like they did in the original paper, but we are not able to customize our data with this code so I used another code later on.

```{r}
enrichment_chart(result_df = DataforEnrichment, top_terms = 20)
```

#Using ggplot to make the enrichment chart with top 20 terms and using a blue color gradient just like the authors did on the original paper.

```{r}
library(ggplot2)
g <- enrichment_chart(DataforEnrichment, top_terms = 20)
g <- g + scale_color_gradient(low = "black", high = "blue")
g
```




